基于卷积神经网络的视觉目标跟踪算法研究

### 2021-03-23 博士/毕业论文/ucasthesis/Tex/Frontmatter.tex
删除音频识别

视觉目标跟踪是计算机视觉领域中最重要和最具挑战性的研究课题之一，在智能监控、自动驾驶等领域有着广阔的应用前景。视觉目标跟踪任务的核心是估计图像序列的每帧中目标的运动状态。目标跟踪是计算机视觉领域的中层部分，为目标的行为理解提供了基础，因此具有非常重要的理论研究价值。同时，它具有广泛的实际应用，包括视频监控、交通流量监控、视频压缩和人机交互等。
然而，目标跟踪领域存在很多理论和技术问题有待解决，如运动模糊、光照变化、非刚性目标的形变、视角的变化导致的目标旋转、遮挡等。近年来深度学习的突破为解决目标跟踪中的一系列问题带来了可能。
深度学习是基于人工神经网络的机器学习方法。在过去的十年中，深度学习技术得到了飞速发展，已成功应用于计算机视觉、语音识别、自然语言处理、音频识别、社交网络过滤、机器翻译、生物信息学、药物设计等领域。如何利用深度学习方法，尤其是深度卷积神经网络解决跟踪过程中遇到的复杂问题，具有较大的研究价值和研究空间。

@@

Visual object tracking is one of the most important and challenging research topics in the field of computer vision, and it has potential and broad application prospects in the fields of intelligent surveillance and autonomous driving. The goal of visual object tracking is to estimate the motion state of the target in each frame of the image sequences. Visual object tracking is the middle level of the computer vision field, which provides a basis for activity understanding, so it has very important theoretical research value. At the same time, it has a wide range of practical applications, including video surveillance, traffic flow monitoring, video compression, and human-computer interaction.
However, there are many theoretical and technical problems to be solved in the field of object tracking, such as motion blur, illumination changes, deformation of non-rigid targets, target rotation and occlusion caused by changes in perspective. In recent years, the breakthrough of deep learning has brought the possibility to solve a series of problems in object tracking.
Deep learning is a machine learning method based on artificial neural networks. In the past ten years, deep learning technology has been rapidly developed and has been successfully applied in computer vision, speech recognition, natural language processing, audio recognition, social network filtering, machine translation, bioinformatics, drug design and other fields. How to use deep learning methods, especially deep convolutional neural networks to solve the complex problems encountered in the tracking process, has great research value and research space.

>>>>

视觉目标跟踪是计算机视觉领域中最重要和最具挑战性的研究课题之一，在智能监控、自动驾驶等领域有着广阔的应用前景。视觉目标跟踪任务的核心是估计图像序列的每帧中目标的运动状态。目标跟踪是计算机视觉领域的中层部分，为目标的行为理解提供了基础，因此具有非常重要的理论研究价值。同时，它具有广泛的实际应用，包括视频监控、交通流量监控、视频压缩和人机交互等。
然而，目标跟踪领域存在很多理论和技术问题有待解决，如运动模糊、光照变化、非刚性目标的形变、视角的变化导致的目标旋转、遮挡等。近年来深度学习的突破为解决目标跟踪中的一系列问题带来了可能。
深度学习是基于人工神经网络的机器学习方法。在过去的十年中，深度学习技术得到了飞速发展，已成功应用于计算机视觉、语音识别、自然语言处理、社交网络过滤、机器翻译、生物信息学、药物设计等领域。如何利用深度学习方法，尤其是深度卷积神经网络解决跟踪过程中遇到的复杂问题，具有较大的研究价值和研究空间。

@@

Visual object tracking is one of the most important and challenging research topics in the field of computer vision, and it has potential and broad application prospects in the fields of intelligent surveillance and autonomous driving. The goal of visual object tracking is to estimate the motion state of the target in each frame of the image sequences. Visual object tracking is the middle level of the computer vision field, which provides a basis for activity understanding, so it has very important theoretical research value. At the same time, it has a wide range of practical applications, including video surveillance, traffic flow monitoring, video compression, and human-computer interaction.
However, there are many theoretical and technical problems to be solved in the field of object tracking, such as motion blur, illumination changes, deformation of non-rigid targets, target rotation and occlusion caused by changes in perspective. In recent years, the breakthrough of deep learning has brought the possibility to solve a series of problems in object tracking.
Deep learning is a machine learning method based on artificial neural networks. In the past ten years, deep learning technology has been rapidly developed and has been successfully applied in computer vision, speech recognition, natural language processing, social network filtering, machine translation, bioinformatics, drug design and other fields. How to use deep learning methods, especially deep convolutional neural networks to solve the complex problems encountered in the tracking process, has great research value and research space.
